% Created 2022-11-02 Wed 20:56
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\date{}
\title{Debate System (Charter)}
\hypersetup{
 pdfauthor={Salh Jabr},
 pdftitle={Debate System (Charter)},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.0.50 (Org mode 9.6)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{Project Metadata}
\label{sec:orgce8ff27}
\begin{itemize}
\item Project Name: Debate System
\item Project Description: A polymathic, multi-feature services that consolidate the structure
of online conversations. Includes a web-client implementation.
\item Data Approved: 03 Nov, 2022.
\end{itemize}
\section{Businesses Case}
\label{sec:org02ffb5e}
\begin{itemize}
\item Current situation of debate platforms:
\begin{itemize}
\item Either too minimal and not unusable (like most image board websites), or;
\item Too bloated and badly designed, and leak substantial features (like Kialo).
\end{itemize}
\item Our objectives are to fulfill the both shortcomings with a platform that is compatible
with multi-typed midea structures.
\end{itemize}
\section{Team Members}
\label{sec:orgc2bc8c6}
\begin{center}
\begin{tabular}{ll}
\hline
Member & Role\\\empty
\hline
Mostafa Rady & Client-side development (front-end)\\\empty
Abdo Muhammed & Server-side development (back-end)\\\empty
Abdallah Salah & Front-end development\\\empty
Salh Mohamed & Services Architecture and Deployment\\\empty
\hline
\end{tabular}
\end{center}
\section{Risk and Constrains}
\label{sec:org8a1718f}
\begin{itemize}
\item In the case of the implementation of external platforms support, that might cause either
complexities in performance, or constrains from those platforms (some platforms might
disable the content out of their domain)
\end{itemize}
\section{Expected Goals}
\label{sec:org2ce6815}
We are anticipating having a semi-complete platform with an appropriate user interface, that
fulfills the mentioned shortcomings.
\section{Scope Description}
\label{sec:org9610aba}
\begin{itemize}
\item In Scope:
\begin{itemize}
\item Interactive debate management that supports interactive arguing.
\item Quoting, arguing and response support.
\end{itemize}
\item Out of scope:
\begin{itemize}
\item Chat support.
\item External platforms conversations support.
\end{itemize}
\end{itemize}
\end{document}